\documentclass[12pt]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\newcommand\red[1]{\textcolor{red}{#1}}

\title{Contributions}

\begin{document}

\maketitle

\section{Preliminary Draft}

Dylan Cordaro: 3.2 to 3.5, ran reddit-binary results, proteins for the GCN architecture. 


Shelby Cox: Implemented the GCN architecture described by the original authors (with help from Yiman and verified by the rest of the group). Wrote 3.1 (Datasets). Contributed to writing Section 5 (Discussion). Wrote the final draft of Section 2 (Scope of Reproducibility) after Teresa wrote drafts of the claims. Tracked down references for proofs the authors used for their proofs of Theorem 4.2 and 4.3. Ran experiments for the PROTEINS dataset using larger augmented graphs.


Yiman Ren: Wrote Section 3.1 Model descriptions and part of section 4.1. Contributed to the implementation of GCN architecture and the understanding of USVT graphon estimation method and the algorithm for multi-class classification synthetic graph generation. Run the authors codes on Colab and tried to replicate the results using REDDIT-BINARY, with environment setup by Dylan. Contributed to revising the draft. 


Teresa Yu: Wrote Sections 1 and 4.1.1 (the first ``result"; wrote the mathematical background/notation and filled-in proofs). Contributed to writing Report Summary and Section 5 (Discussion), and contributed to editing the overall draft. Contacted authors of the paper to potentially ask them our questions.


Everyone: Contributed to understanding mathematical content of paper and explaining to each other; compared paper with paper authors' code and identified inconsistencies; came up with interesting potential experiments to extend paper's results; discussed the replication results and the possible solutions to problems coming up in replications and experiments.

\textbf{Paragraph:}

Everyone in the group contributed to understanding the theoretical and mathematical content as well as the algorithm proposed of the paper. We all contributed to comparing the paper with the authors' provided code and identified inconsistencies, and we all contributed to implementing the GCN architecture. We all contributed to coming up with ideas for experiments extending the paper. Dylan contributed to writing Sections 3.2--3.5 and running the actual experiments on the datasets. Shelby contributed to writing Sections 2, 3.2, 4.2, and 5, and the summary, as well as the running of the actual experiments on the datasets. Yiman contributed to writing Section 3.1 and 4.1, revising and polishing the overall draft, understanding the graphon estimator, and running the actual experiments on the datasets. Teresa contributed to writing and editing all of the sections of the report as well as the summary (including writing the more-complete proof of the theoretical result); she also contacted the original paper's authors.


\end{document}