\documentclass{amsart}

\usepackage{hyperref}

\title{Reviews/Feedback}

\begin{document}

The reviews can be accessed at this link: \href{https://umich-eecs553fa22.hotcrp.com/paper/15}{https://umich-eecs553fa22.hotcrp.com/paper/15}.

\begin{itemize}
    \item In summary page (and in main paper): it would be nice to say who the authors/ works were instead of JUST the number citation. Using just the number is more ok if your not using said number as a word in the sentence
    
    \item In summary page: methodology - first sentence is wordy and should be reworked
    
    \item If you leave a whole blank line between paragraphs then the paper should format in a way that is easier to read
    
    \item 3.4 If you want to number your loss equation you can use: (same for section 4) begin{equation} loss equation here end{equation}
    
    \item 4.1 The ||W|| have little boxes next to them, are these supposed to be there?
    
    \item Great work on filling the gap of the theoretical proof in the original paper. 
    
    \item The sizes of the figures could be larger to make them more readable.
    
    \item The scope of reproducibility is explained to a very limited extent and could be elaborated more in the final report.

    \item Noticeable redundancy throughout the report explaining the same concept repeatedly. This makes the report long to read as well. The results part could also be made a bit more to the point.

    \item Formatting error - Noticed boxes as subscripts in mathematical equations throughout the paper.

    \item The most difficult part was mentioned to be making the code run for bigger datasets and managing memory efficiently, this was also said to be tackled to an extent in the methodology section. More insights as to how this problem was overcome could be mentioned which will elaborate the efforts even more.

    \item The report is very well-written, I can see that this group put in a lot of time in doing the project and writing their report. 
    
    \item Maybe a suggestion for the report would be to mention the changes you made due to memory issues either in 3.1, where you mention changes were made, or in 3.4 where you discuss how to replicate your experiments, on top the explanation regarding this in sec 5 that you currently have. 
    
    \item It would also be nice to explain a bit on how the G-mixup ties into improving the performance of GNNs, maybe in sec 3.

    \item The authors overall understand the original paper very well. 
    
    \item Y label of Figure 2 is missing (I guess it is cross entropy loss?) 
    
    \item One of the main claim is related to cross entropy so it is important to provide more more details about original cross entropy loss.

    \item This group has a very good understanding of the theory behind graph neural network and the introduced data augmentation method in the original paper.

    \item Great work! The report is well-organized. The authors summarize the major contributions of the original paper clearly. Theories explain and results reproduction present in a logical way. I look forward to seeing further updates (if I can).

    \item The authors have a good understanding of the original paper. The report is well-written, with detailed experiments. I like the way the authors provided mathematical analysis for the theory in the original paper. 
    
    \item It would be nice if the authors could provide experiments for more datasets.
\end{itemize}

There are a few things that appear multiple times:
\begin{itemize}
    \item The boxes in the notation for the cut norm -- they should be there! Maybe we should make a note of this near the definition of cut norm.
\end{itemize}

\end{document}