\section*{\centering Reproducibility Summary}
\subsubsection*{Scope of Reproducibility}

This study aims to reproduce the results of the paper 'FOCUS: Flexible Optimizable Counterfactual Explanations for Tree Ensembles' by Lucic et al.\cite{lucic2022focus}.
The main claims of the original paper are that FOCUS is able to (i) generate counterfactual explanations for all the instances in a dataset; 
and (ii) find counterfactual explanations that are closer to the original input for tree-based algorithms than existing methods.

\subsubsection*{Methodology}
This study replicates the original experiments using the code, data, and models provided by the authors. Additionally, this study re-implements code and retrains the models to evaluate the robustness and generality of FOCUS.
All the experiments were conducted on a personal laptop with a quad-core CPU with 8GB of RAM and it approximately took 33 hours in total.

\subsubsection*{Results}
This study was able to replicate the results of the original paper in terms of finding counterfactual explanations for all instances in datasets. Additional experiments were conducted to validate the robustness and generality of the conclusion. While there were slight deviations in terms of generating smaller mean distances, half of the models still outperformed the results of the existing method.

\subsubsection*{What was easy}
The implementation of the original paper is publicly available on GitHub. The repository contains the models and data used in the original experiments. Also, the authors provided a technical appendix, which includes all hyperparameters that were used for the experiments for reproduction upon request. 

\subsubsection*{What was difficult}
Although the implementation code was available, it employs outdated packages and the code structure is complex. Also, the comments in the functions and the documentation of the code are sparse or nonexistent, which made it difficult to follow the code.

\subsubsection*{Communication with original authors}
I reached out to the authors to obtain the hyperparameters used in the experiments. The authors responded promptly with a detailed technical appendix of the original paper.
